The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources

### 2020-01-02 paper.tex
Modified Black Hole Luminosity text and equations; uploaded modified L_x histogram and lognormal plot.

@@

The net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019MNRAS.486.5377I}:
\begin{equation}
    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
\end{equation}
where M is black hole mass, G is the gravitational constant, and v is the black hole velocity.

Finally, the black hole x-ray luminosity is estimated from:
\begin{equation}
    L_x = 0.01\dot{M}_{acc}c^2 \text{  erg s}^{-1}.
\end{equation}

The Eddington limit is defined as:
\begin{equation}
    L_{edd} = 1.26 \times 10^{38} (M/M_{\odot}) \text{  erg s}^{-1}.
\end{equation}

>>>>

THIS SECTION TAKEN VERBATIM FROM \citet{2017MNRAS.467.4180S}, SECTION E1.  NEED TO MODIFY.

@@

The net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019MNRAS.486.5377I}:
\begin{equation}
    \dot{M}_{acc} = f\frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
\end{equation}
where f is a factor giving the decline in accretion, interior to the BH radius due to convective (i.e., inefficient) accretion, as calculated \citet{2019MNRAS.486.5377I}, cf. eq 13.  Additionally, $M$ is black hole mass, $G$ is the gravitational constant, and $v$ is the black hole velocity.

Finally, the black hole x-ray luminosity is estimated from:
\begin{equation}
    L_x = \epsilon_{rx}\dot{M}_{acc}c^2 \text{  erg s}^{-1},
\end{equation}
where the x-ray radiative efficiency ${\epsilon}_{rx}=0.01$, and we are assuming for the low-luminosity sources that $L_B{\sim}L_x$.  For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$.
The Eddington limit is defined as:
\begin{equation}
    L_{edd} = 1.26 \times 10^{38} (M/M_{\odot}) \text{  erg s}^{-1}.
\end{equation}
